---
title: "DOP NPS Trends"
output: html_document
date: "2023-02-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include = FALSE}
# accounts <- read.csv("C:/Users/matthew.sherrick/Downloads/Boost DOP NPS Accounts.csv")  # 6149
# survey <- read.csv("C:/Users/matthew.sherrick/Downloads/Boost DOP NPS Survey.csv")      # 6268
# 
# DOP <- merge(accounts, survey, by = "CUSTOMER_ACCOUNT_SK")                              # 6268
# 
# # write.csv(DOP,"DOP2.csv")
# 
# n_distinct(accounts$CUSTOMER_ACCOUNT_SK)
# n_distinct(survey$CUSTOMER_ACCOUNT_SK)
# 
# n_distinct(DOP$CUSTOMER_ACCOUNT_SK)

DOP <- read.csv("C:/Users/matthew.sherrick/Documents/DOP2.csv")

DOP$endDate <- as.Date(DOP$endDate, format = "%m/%d/%Y")
```

```{r, include = FALSE}
library(lubridate)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(plotly)

#####################
# Average NPS by week
weekly <- DOP %>%
  group_by(week = cut(endDate, "week")) %>%
  mutate(weeklyNPS = mean(NPS)) %>%
  dplyr::select(week,weeklyNPS) %>%
  arrange(desc(week))

weekly
  
data <- weekly %>%
  group_by(week) %>%
  summarize(NPS = mean(weeklyNPS)) %>%
  arrange(desc(week))

data

data$week <- as.Date(data$week)

ggplot(data, aes(x = week, y = NPS)) + geom_line()
##################
```
The following plots show the trend of weekly NPS based on the 8 variables of interest: New vs. Tenure (0-6 months vs > 6 mo.), DOP migrated vs Not, BYOD vs Buy, Autopay, OS Apple vs. Android, Sales Channel (E-Commerce, Indirect or National Retail), Single vs. Multiline, and MRC Amount (in $10 buckets). I also included additional slices worth looking into, like plan type, network provider (AT&T vs T-Mobile), and port status The first set of 8 plots display the all time survey data, and the later set just focuses on the latest 6-week period.

# All-Time Survey Data

```{r, message = FALSE, echo = FALSE}
# plots
slice <- DOP %>%
  group_by(week = cut(endDate, "week")) %>%
  mutate(weeklyNPS = mean(NPS))

# BYOD
p <- slice %>%
  select(ORDER_DEV_BYOD, week, NPS) %>%
  group_by(week, ORDER_DEV_BYOD) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = ORDER_DEV_BYOD, color = as.factor(ORDER_DEV_BYOD))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by BYOD Orders", subtitle = "Blue = BYOD, Red = Device Purchase")
  
ggplotly(p)

# Migrated
p <- slice %>%
  select(MIGRATED_FLAG, week, NPS) %>%
  group_by(week, MIGRATED_FLAG) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = MIGRATED_FLAG, color = as.factor(MIGRATED_FLAG))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Migration Status", subtitle = "Blue = Migrated, Red = Not Migrated")

ggplotly(p)
# autopay
p<- slice %>%
  select(ACCT_AUTOPAY, week, NPS) %>%
  group_by(week, ACCT_AUTOPAY) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = ACCT_AUTOPAY, color = as.factor(ACCT_AUTOPAY))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by AutoPay Status", subtitle = "Blue = AutoPay, Red = No AutoPay")

ggplotly(p)
# order channel
p <- slice %>%
  select(ORDER_CHANNEL, week, NPS) %>%
  group_by(week, ORDER_CHANNEL) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = ORDER_CHANNEL, color = as.factor(ORDER_CHANNEL))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Order Channel", subtitle = "Red = E-Commerce, Green = Indirect, Blue = National Retail, Purple = Unknown")

ggplotly(p)
# num of lines
multiline.slice <- subset(slice, !is.na(NUMBER_OF_ACTIVE_LINES)) 

p <- multiline.slice %>%
  select(NUMBER_OF_ACTIVE_LINES, week, NPS) %>%
  group_by(week, NUMBER_OF_ACTIVE_LINES) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = NUMBER_OF_ACTIVE_LINES, color = as.factor(NUMBER_OF_ACTIVE_LINES))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Number of Lines", subtitle = "Red = 1 Line, Yellow Green = 2, Green = 3, Blue = 4, Purple = 5")
ggplotly(p)
# device OS
os.slice <- subset(slice, !is.na(DEV_OS))

p<- os.slice %>%
  select(DEV_OS, week, NPS) %>%
  group_by(week, DEV_OS) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = DEV_OS, color = as.factor(DEV_OS))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Device OS", subtitle = "Red = Android, Blue = Apple")
ggplotly(p)

# Tenure

p <- slice %>%
  select(Tenure, week, NPS) %>%
  group_by(week, Tenure) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = Tenure, color = as.factor(Tenure))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Tenure", subtitle = "Red = New (0 - 6 Months), Blue = Tenured (6+ Months)")
ggplotly(p)

# MRC
p<-slice %>%
  select(MRC.Bin, week, NPS) %>%
  group_by(week, MRC.Bin) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = MRC.Bin, color = as.factor(MRC.Bin))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1)) +
  scale_color_manual(values = c('red2', 'orange3', 'yellow3', 'green3', 'cyan3', 'purple2', 'pink')) +
  labs(title = "Average Weekly NPS by MRC", subtitle = "Red = $0-10, Orange = $11-20, Yellow = $21-30, Green = $31-40, Blue = $41-50, Purple = $51-60, Pink = $61+") +
  theme(plot.subtitle = element_text(size = 8))
  
ggplotly(p)
# # Plan type
# 
# slice["ORDER_PLAN"][slice["ORDER_PLAN"] == ''] <- NA
# slice.plan <- subset(slice, !is.na(ORDER_PLAN))
# 
# slice.plan %>%
#   select(ORDER_PLAN, week, NPS) %>%
#   group_by(week, ORDER_PLAN) %>%
#   summarize(NPS = mean(NPS)) %>%
#   ggplot(aes(x = week, y = NPS, group = ORDER_PLAN)) + geom_line(show.legend = TRUE) +
#   theme(axis.text.x = element_text(angle=90, hjust =1, size = 7)) +
#   facet_wrap(~ORDER_PLAN) +
#   theme(strip.text.x = element_text(size = 7)) +
#   labs(title = "Average Weekly NPS by Plan Type")

# network provider
p <- slice %>%
  select(network_provider_name, week, NPS) %>%
  group_by(week, network_provider_name) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = network_provider_name, color = as.factor(network_provider_name))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Network Provider", subtitle = "Red = AT&T, Blue = T-Mobile, Green = DISH (Genesis)")
ggplotly(p)

# Port In
p <- slice %>%
  select(PORT_IN, week, NPS) %>%
  group_by(week, PORT_IN) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = PORT_IN, color = as.factor(PORT_IN))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Port Status", subtitle = "Blue = Port In, Red = No Port")
ggplotly(p)

# Plan type - strategic plan code

slice["STRATEGIC_PRICE_PLAN_NAME_CODE"][slice["STRATEGIC_PRICE_PLAN_NAME_CODE"] == ''] <- NA
slice.plan <- subset(slice, !is.na(STRATEGIC_PRICE_PLAN_NAME_CODE))

p <- slice.plan %>%
  select(STRATEGIC_PRICE_PLAN_NAME_CODE, week, NPS) %>%
  group_by(week, STRATEGIC_PRICE_PLAN_NAME_CODE) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = STRATEGIC_PRICE_PLAN_NAME_CODE)) + geom_line(show.legend = TRUE) +
  theme(axis.text.x = element_text(angle=90, hjust =1 )) +
  facet_wrap(~STRATEGIC_PRICE_PLAN_NAME_CODE) +
  theme(strip.text.x = element_text(size = 7)) +
  labs(title = "Average Weekly NPS by Plan Type")
ggplotly(p)
```



# Most Recent 6 Weeks

```{r, echo = FALSE, message = FALSE}
# 6 week slice
slice <- DOP %>%
  group_by(week = cut(endDate, "week")) %>%
  mutate(weeklyNPS = mean(NPS))

six.week <- slice %>%
  filter(endDate > '2023-01-08')

six.week <- six.week %>%
  filter(endDate < '2023-02-14')
  
  
# plots
# BYOD
p<-six.week %>%
  select(ORDER_DEV_BYOD, week, NPS) %>%
  group_by(week, ORDER_DEV_BYOD) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = ORDER_DEV_BYOD, color = as.factor(ORDER_DEV_BYOD))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by BYOD Orders", subtitle = "Blue = BYOD, Red = Device Purchase")
ggplotly(p)

# Migrated
p<-six.week %>%
  select(MIGRATED_FLAG, week, NPS) %>%
  group_by(week, MIGRATED_FLAG) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = MIGRATED_FLAG, color = as.factor(MIGRATED_FLAG))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Migration Status", subtitle = "Blue = Migrated, Red = Not Migrated")
ggplotly(p)

# autopay
p<-six.week %>%
  select(ACCT_AUTOPAY, week, NPS) %>%
  group_by(week, ACCT_AUTOPAY) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = ACCT_AUTOPAY, color = as.factor(ACCT_AUTOPAY))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by AutoPay Status", subtitle = "Blue = AutoPay, Red = No AutoPay")
ggplotly(p)

# order channel
p<-six.week %>%
  select(ORDER_CHANNEL, week, NPS) %>%
  group_by(week, ORDER_CHANNEL) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = ORDER_CHANNEL, color = as.factor(ORDER_CHANNEL))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Order Channel", subtitle = "Red = E-Commerce, Green = Indirect, Blue = National Retail, Purple = Unknown")
ggplotly(p)

# num of lines
multiline.six.week <- subset(six.week, !is.na(NUMBER_OF_ACTIVE_LINES)) 

p<-multiline.six.week %>%
  select(NUMBER_OF_ACTIVE_LINES, week, NPS) %>%
  group_by(week, NUMBER_OF_ACTIVE_LINES) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = NUMBER_OF_ACTIVE_LINES, color = as.factor(NUMBER_OF_ACTIVE_LINES))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  scale_color_manual(values = c('red2', 'orange3', 'green3', 'cyan3', 'purple2')) +
  labs(title = "Average Weekly NPS by Number of Lines", subtitle = "Red = 1 Line, Orange = 2, Green = 3, Blue = 4, Purple = 5")
ggplotly(p)

# device OS
os.six.week <- subset(six.week, !is.na(DEV_OS))

p<-os.six.week %>%
  select(DEV_OS, week, NPS) %>%
  group_by(week, DEV_OS) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = DEV_OS, color = as.factor(DEV_OS))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Device OS", subtitle = "Red = Android, Blue = Apple")
ggplotly(p)

# Tenure

p<-six.week %>%
  select(Tenure, week, NPS) %>%
  group_by(week, Tenure) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = Tenure, color = as.factor(Tenure))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Tenure", subtitle = "Red = New (0 - 6 Months), Blue = Tenured (6+ Months)")
ggplotly(p)

# MRC
p<- six.week %>%
  select(MRC.Bin, week, NPS) %>%
  group_by(week, MRC.Bin) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = MRC.Bin, color = as.factor(MRC.Bin))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1)) +
  scale_color_manual(values = c('red2', 'orange3', 'yellow3', 'green3', 'cyan3', 'purple2', 'pink')) +
  labs(title = "Average Weekly NPS by MRC", subtitle = "Red = $0-10, Orange = $11-20, Yellow = $21-30, Green = $31-40, Blue = $41-50, Purple = $51-60, Pink = $61+") +
  theme(plot.subtitle = element_text(size = 8))
ggplotly(p)
  
# Plan type - order plan

# six.week["ORDER_PLAN"][six.week["ORDER_PLAN"] == ''] <- NA
# six.week.plan <- subset(six.week, !is.na(ORDER_PLAN))
# 
# six.week.plan %>%
#   select(ORDER_PLAN, week, NPS) %>%
#   group_by(week, ORDER_PLAN) %>%
#   summarize(NPS = mean(NPS)) %>%
#   ggplot(aes(x = week, y = NPS, group = ORDER_PLAN)) + geom_line(show.legend = TRUE) +
#   theme(axis.text.x = element_text(angle=90, hjust =1 )) +
#   facet_wrap(~ORDER_PLAN) +
#   theme(strip.text.x = element_text(size = 7)) +
#   labs(title = "Average Weekly NPS by Plan Type")

# network provider
p<-six.week %>%
  select(network_provider_name, week, NPS) %>%
  group_by(week, network_provider_name) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = network_provider_name, color = as.factor(network_provider_name))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Network Provider", subtitle = "Red = AT&T, Blue = T-Mobile)")
ggplotly(p)

# Port In
p<-six.week %>%
  select(PORT_IN, week, NPS) %>%
  group_by(week, PORT_IN) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = PORT_IN, color = as.factor(PORT_IN))) + geom_line(show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=45, hjust =1 )) +
  labs(title = "Average Weekly NPS by Port Status", subtitle = "Blue = Port In, Red = No Port")
ggplotly(p)

# Plan type - strategic plan code

six.week["STRATEGIC_PRICE_PLAN_NAME_CODE"][six.week["STRATEGIC_PRICE_PLAN_NAME_CODE"] == ''] <- NA
six.week.plan <- subset(six.week, !is.na(STRATEGIC_PRICE_PLAN_NAME_CODE))

p<-six.week.plan %>%
  select(STRATEGIC_PRICE_PLAN_NAME_CODE, week, NPS) %>%
  group_by(week, STRATEGIC_PRICE_PLAN_NAME_CODE) %>%
  summarize(NPS = mean(NPS)) %>%
  ggplot(aes(x = week, y = NPS, group = STRATEGIC_PRICE_PLAN_NAME_CODE)) + geom_line(show.legend = TRUE) +
  theme(axis.text.x = element_text(angle=90, hjust =1 )) +
  facet_wrap(~STRATEGIC_PRICE_PLAN_NAME_CODE) +
  theme(strip.text.x = element_text(size = 7)) +
  labs(title = "Average Weekly NPS by Plan Type")
ggplotly(p)
```